Fig5

### 2020-05-09 analysis/figure-4.Rmd
fig 4 updates
small tests working. like these new plots

b1 <- plotcandidatemanipquad(candidatevsd, "hypothalamus", c("DRD1")) 
b2 <- plotcandidatemanipquad(candidatevsd2,"pituitary", c("PRL")) 
b3 <- plotcandidatemanipquad(candidatevsd,"gonad", c("PGR"))

@@

plot_grid(a, bc, ncol = 1, rel_heights  = c(0.25,1),
          labels = "AUTO", label_size = 8)

>>>>

b1 <- plotcandidatemanipquad(candidatevsd, "hypothalamus", c("DRD1")) 
b2 <- plotcandidatemanipquad(candidatevsd,"pituitary", c("PRL")) 
b3 <- plotcandidatemanipquad(candidatevsd,"gonad", c("PGR"))

@@

fig4 <- plot_grid(a, bc, ncol = 1, rel_heights  = c(0.25,1),
          labels = "AUTO", label_size = 8)
fig4

pdf(file="../figures/fig4-1.pdf", width=7.25, height=7.25)
plot(fig4)
dev.off()

candidatevsd <- candidatevsd %>%
  dplyr::mutate(treatment = fct_collapse(treatment,
                                         "m.n2" = c("m.n2",  "m.hatch" ),
                                         "prolong" = c("prolong", "inc.prolong") ,
                                         "extend" = c("extend", "extend.hatch")
                                         ))  %>%
  dplyr::mutate(day = fct_collapse(treatment,
                                    "0" = c("control", "bldg"),
                                    "1" = c("lay"),
                                     "3" = c("inc.d3", "m.inc.d3" ),
                                     "9" = c("inc.d9", "m.inc.d9", "m.inc.d8"  ),
                                     "17" = c("inc.d17", "m.inc.d17", "prolong"  ),
                                     "18" = c("hatch", "m.n2" ),
                                     "22" = c("n5",  "extend" ),
                                     "26" = c("n9"  )
                                     )) %>%
   mutate(treatment = factor(treatment, levels = alllevels)) %>%
  dplyr::mutate(day = factor(day, levels = c("0", "1", "3", "9", "17", "18", "22", "26")))

candidatevsd %>%
    filter(tissue == "hypothalamus", sex == "female") %>%
    filter(gene %in% "DRD1") %>%
    drop_na()  %>%
    ggplot(aes(y =  counts, x = day, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "bottom",
          #axis.text.x = element_blank(),
          #axis.title.x = element_blank(),
          strip.text = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(subtitle = paste("female", "hypothalamus", sep = " "), y = "DRD1")

candidatevsd %>%
    filter(tissue == "pituitary", sex == "female") %>%
    filter(gene %in% "PRL") %>%
    drop_na()  %>%
    ggplot(aes(y =  counts, x = day, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "bottom",
          #axis.text.x = element_blank(),
          #axis.title.x = element_blank(),
          strip.text = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(subtitle = paste("female", "pituitary", sep = " "), y = "PRL")
